---
title: "Tutorial!"
author: "Augustina Ragwitz"
date: "October 16, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r includes, message=FALSE}
library(dplyr)
library(gutenbergr)
library(tidytext)
library(ggplot2)
library(stringr)
library(tidyverse)
```

```{r}


full_text <- gutenberg_download(4300)

tidy_book <- full_text %>% 
  mutate(line=row_number()) %>% 
  unnest_tokens(word,text)

# count words
tidy_book_count <- tidy_book %>% count(word, sort=TRUE)

# remove common words using an anti_join
tidy_book_count_stop <- tidy_book %>% anti_join(stop_words) %>% count(word, sort=TRUE)

```

```{r}
tidy_book_top <- tidy_book %>%
  anti_join(stop_words) %>%
  filter(! str_detect(word, "'")) %>%
  filter(! str_detect(word, "’")) %>%
  count(word, sort = TRUE) %>%
  top_n(30) %>%
  mutate(word=reorder(word,n))

ggplot(tidy_book_top, aes(x=word, y=n)) +
  geom_bar(stat="identity") +
  coord_flip()
```

```{r}
tidy_book_bow <- tidy_book %>% 
  inner_join(get_sentiments("bing")) %>%
  count(sentiment, word, sort = TRUE) %>%
  group_by(sentiment) %>%
  top_n(20) %>%
  ungroup %>%
  mutate(word=reorder(word,n))

ggplot(tidy_book_bow, aes(x=word, y=n, fill=sentiment))+
  geom_col(stat="identity", show.legend = FALSE) +
  coord_flip() +
  facet_wrap(~ sentiment, scales = "free")
  
```

TFIDF -> What is a document about? tf * idf
Term Frequency <- how often a document uses a word
IDF <- ratio of word to documents in a collection of documents
idf(term) = ln( n documents / n documents containing term)
^^ "weight" to compare words within a collection ^^

```{r}

full_collection <- gutenberg_download(c(4300, 2814, 4217, 2817), meta_fields = "title")

full_collection %>% count(title)
```

```{r}
book_words <- full_collection %>%
  unnest_tokens(word, text) %>%
  count(title, word, sort = TRUE) # input into tfidf

book_words
```
```{r}
book_words <- book_words %>% filter(! str_detect(word, "'")) %>% bind_tf_idf(word, title, n) %>% arrange(-tf_idf)

book_words
```

```{r}
ggplot(book_words %>% top_n(10), aes(x=word, y=n, fill=title)) +
  geom_col(stat="identity", show.legend = FALSE) +
  facet_wrap(~ title, scales = "free") +
  coord_flip()
```

```{r}
tidy_ngram <- full_text %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)

tidy_ngram
```

```{r}
tidy_ngram <- tidy_ngram %>%
  separate(bigram, c("word1", "word2"), sep=" ") %>%
  filter(!word1 %in% stop_words$word, !word2 %in% stop_words$word) %>%
  count(word1, word2, sort = TRUE)

tidy_ngram
  
```


```{r}
# words with he/she
he_she <- full_text %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  separate(bigram, c("word1", "word2"), sep=" ") %>%
  filter(word1 %in% c("he", "she")) %>%
  filter(!word2 %in% stop_words$word, !str_detect(word2, "'")) %>%
  count(word1, word2, sort=TRUE)

he_she

```

```{r}
he_she_top <- he_she %>% group_by(word1) %>% top_n(20)

ggplot(he_she_top, aes(x=word2, y=n, fill=word1)) +
  geom_bar(stat="identity", show.legend = FALSE) +
  coord_flip() +
  facet_wrap(~ word1, scales="free")
```


